Using spatially biased variables in ecosystem condition accounting with a GIS based workflow

### 2024-02-22 manuscript/HIAs.qmd

```{r import}
#| cache: true

@@

# Mire data
mire_terra <- terra::rast(path_mire)

@@

@@

```{r mireTerra}
#| eval: true

# I first tried to import and crop the mire data using starts, but that failed (se pre 21 feb 2023)
# trying { terra } instead

@@

# Plot to check overlap
# ggplot()+
#  geom_spatraster(data = mire_nf_terra)+
#  geom_spatvector(data = nf_vect,
#                  fill = NA)
# The cropping and masking worked.

# I like the stars, sf and tmap combo better, so I return to stars
mire_stars_nf <- mire_terra_nf |>
  st_as_stars()
mire_stars_gr <- mire_terra_gr |>
  st_as_stars()
mire_stars_na <- mire_terra_na |>
  st_as_stars()

@@

@@

```{r dk2-CoverageMaps}
#| eval: false

@@

```{r mireArea}
#| eval: false

@@

# Make a plot to check that it has worked
infraMuni3_tbl |>
  ggplot() +
  geom_bar(
    aes(
      x = infrastructureIndex,
      y = total_area_HIAs_km2,
      fill = factor(infrastructureIndex),
      colour = factor(infrastructureIndex)
    ),
    stat = "identity",
    lwd = 1.2
  ) +
  scale_fill_manual(values = RColorBrewer::brewer.pal(4, "YlOrBr")) +
  scale_color_manual(values = RColorBrewer::brewer.pal(5, "YlOrBr")[-1]) +
  theme_minimal_hgrid() +
  labs(
    x = "Human Impact Area (HIA) class",
    y = "Area (km<sup>2</sup>)"
  ) +
  theme(
    axis.title.x = element_textbox_simple(
      width = NULL,
      padding = margin(4, 4, 4, 4),
      margin = margin(4, 0, 0, 0),
      linetype = 1,
      r = grid::unit(8, "pt"),
      fill = "azure1"
    ),
    axis.title.y = element_textbox_simple(
      width = NULL,
      padding = margin(4, 4, 4, 4),
      margin = margin(4, 0, 0, 0),
      linetype = 1,
      orientation = "left-rotated",
      r = grid::unit(8, "pt"),
      fill = "azure1"
    ),
    strip.background = element_blank(),
    strip.text = element_textbox(
      size = 12,
      color = "white", fill = "#5D729D", box.color = "#4A618C",
      halign = 0.5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
      padding = margin(2, 0, 1, 0), margin = margin(3, 3, 3, 3)
    )
  ) +
  guides(fill = "none", colour = "none") +
  scale_y_log10() +
  facet_grid(cols = vars(Municipality))
```
```{r corrCheck}
#| eval: true
# Now I want to see if the indicator values depend on the HIA is a predictable
# way to justify the stratification
corrCheck <- st_intersection(naturetypes, infra)

@@

```{r}
#| eval: false
# The year effect is constant, so ignoring that
corrCheck |>
  mutate(
    i_ADSV_fct = floor(round(i_ADSV * 10, 2)) / 10,
    i_alien_fct = floor(round(i_alien * 10, 2)) / 10,
    i_ditch_fct = floor(round(i_ditch * 10, 2)) / 10
  ) |>
  pivot_longer(
    cols = c(i_ADSV_fct, i_alien_fct, i_ditch_fct),
    values_to = "indicatorValue",
    names_to = "indicator",
    values_drop_na = T
  ) |>
  ggplot(aes(
    x = factor(infrastructureIndex),
    fill = factor(indicatorValue)
  )) +
  geom_bar(
    position = "fill"
  ) +
  theme_bw(base_size = 12) +
  guides(fill = guide_legend("Scaled indicator values")) +
  ylab("Fraction of data points") +
  xlab("HIA") +
  scale_fill_brewer(
    palette = "RdYlGn") +
  facet_grid(~indicator)
```

```{r}
#| eval: true
# Using a color gradient emphasizes the first color (dark green).
# Lets try discrete colors, and merge som classes to simplify
(validationPlot <- corrCheck |>
  #rename(ADSV = i_ADSV) |>
  pivot_longer(
    cols = c(i_ADSV, i_alien, i_ditch),
    values_to = "indicatorValue",
    names_to = "indicator",
    values_drop_na = T
  ) |>
  mutate(
    condition = case_when(
      indicatorValue < 0.6 ~ "<0.6",
      indicatorValue < 0.8 ~ "0.6 to 0.8",
      indicatorValue < 0.91 ~ "0.8 to 0.9",
      .default = "0.9 to 1"
    ),
    condition = fct_reorder(condition, indicatorValue),
    indicator = case_when(
      indicator == "i_ADSV" ~ "ADSV",
      indicator == "i_alien" ~ "Alien species",
      indicator == "i_ditch" ~ "Trenching"
    )
  ) |>
  ggplot(aes(
    x = factor(infrastructureIndex),
    fill = condition
  )) +
  geom_bar(
    position = "fill"
  ) +
  theme_bw(base_size = 12) +
  guides(fill = guide_legend("Indicator values")) +
  ylab("Fraction of data points") +
  xlab("Human Impact Areas") +
  scale_fill_brewer(palette = "RdYlGn") +
  facet_grid(~indicator)
)
```

```{r}
#| eval: false
# The figure changes a lot depending on which value gets the darker colour
corrCheck |>
  pivot_longer(
    cols = c(i_ADSV, i_alien, i_ditch),
    values_to = "indicatorValue",
    names_to = "indicator",
    values_drop_na = T
  ) |>
  mutate(
    condition = case_when(
      indicatorValue < 0.6 ~ "Poor",
      indicatorValue < 0.8 ~ "Intermediate",
      indicatorValue < 0.91 ~ "Good",
      .default = "Perfect"
    ),
    condition = fct_reorder(condition, -indicatorValue)
  ) |>
  ggplot(aes(
    x = factor(infrastructureIndex),
    fill = condition
  )) +
  geom_bar(
    position = "fill"
  ) +
  theme_bw(base_size = 12) +
  guides(fill = guide_legend("Scaled indicator values")) +
  ylab("Fraction of data points") +
  xlab("HIA") +
  scale_fill_viridis_d(alpha = .8) +
  facet_grid(~indicator)
```

```{r}
#| eval: false
# If I look at this on a log scale, it also changes and becomes less convincing for ADSV and alien
corrCheck |>
  pivot_longer(
    cols = c(i_ADSV, i_alien, i_ditch),
    values_to = "indicatorValue",
    names_to = "indicator",
    values_drop_na = T
  ) |>
  mutate(
    condition = case_when(
      indicatorValue < 0.6 ~ "Poor",
      indicatorValue < 0.8 ~ "Intermediate",
      indicatorValue < 0.91 ~ "Good",
      .default = "Perfect"
    ),
    condition = fct_reorder(condition, -indicatorValue)
  ) |>
  ggplot(aes(
    x = factor(infrastructureIndex),
    fill = condition
  )) +
  geom_bar(
    position = "fill"
  ) +
  theme_bw(base_size = 12) +
  guides(fill = guide_legend("Scaled indicator values")) +
  ylab("Fraction of data points") +
  xlab("HIA") +
  scale_y_log10() +
  scale_fill_viridis_d(alpha = .8) +
  facet_grid(~indicator)

@@

```{r}
#| eval: false

@@

```{r infraMuniMaps}
#| eval: false

# Infratructure in each municipality
infraMuniMap <- tm_shape(muni3) +
  tm_borders() +
  tm_shape(infraMuni3) +
  tm_polygons(
    col = "infrastructureIndex",
    style = "cat",
    title = "Human Impact\nArea Class"
  ) +
  tm_shape(muni3) +
  tm_borders(lwd = 3, col = "black") +
  tm_facets(by = "Municipality") +
  tm_layout(
    legend.show = FALSE,
    panel.label.height = 0)

# A figure with just the legend
infraMuniMap_l <- tm_shape(muni3) +
  tm_borders() +
  tm_shape(infraMuni3) +
  tm_polygons(
    col = "infrastructureIndex",
    style = "cat",
    title = "Human\nImpact\nArea"
  ) +
  tm_layout(legend.only = TRUE,
            legend.position = c("left", "bottom"),
            legend.outside = TRUE)

@@

(methodsMap <- tmap_arrange(
  positionMap,
  muniPlot,
  infraMuniMap_l,
  infraMuniMap,
  widths = c(.35, .65),
  heights = c(.6, .4),
  outer.margins = NULL
))

@@

# Calulate some more stats for the table with municipality stats

@@

# Take muni3 and add all sorts of other data to it
# using left_join.
# Save local cached file
muni_tbl <- muni3 |>
  # calculate total area
  mutate(
    area_km =
      round(
        units::drop_units(
          geom |> st_area() * 1e-6
        )
      )
  ) |>
  # make tibble for the coming join
  as_tibble() |>
  # paste inn terrestrial area
  left_join(terrestrial |>
              as_tibble() |> 
              select(kommunenummer, t_area_km),
    keep = F
  ) |>
  # area of survey
  left_join(dk2 |> select(Municipality, dk_area_km)) |>
  mutate(dk_percent = round((dk_area_km / t_area_km) * 100)) |>
  # number of polygons
  left_join(nature3_tbl |> select(Municipality, n)) |>
  # total mire area and %
  left_join(mireArea |> select(Municipality, mirePercent, mire_km2)) |>
  # % mire inside survey coverage map
  left_join(mire_nf_terra_dk |> select(Municipality, mireInSurvey_km2)) |>
  mutate(mireInSurvery_percent = round(mireInSurvey_km2 / mire_km2 * 100, 2)) |>
  left_join(infraMuni3_summary)

@@

| id  | Variable code        | Variable name                                    | Measurement unit                                                                        | Description                                                                                                                                                       | Reference                          |
|-----|----------------------|--------------------------------------------------|-----------------------------------------------------------------------------------------|-------------------------------------------------------------------------------------------------------------------------------------------------------------------|------------------------------------|
| 1   | 7FK                  | Prevalence of alien species                      | Unitless, ordinal, non-linear scale from 1 (no alien species) to 7 (only alien species) | The fraction of the species composition made up from alien species                                                                                                | @runehalvorsen2019                 |
| 2   | 7SE                  | Human caused abration or abration-caused erosion | Unitless, ordinal, non-linear scale from 1 to 4.                                        | Measures the frequency of imagined 4 m^2^ quadrats layed over the area that has some sign of abration                                                             | @runehalvorsen2019                 |
| 3   | PRSL                 | *as above*                                       | Unitless, ordinal, non-linear scale from 0 to 7.                                        | Same as 7SE, but recorded at a higher resolution                                                                                                                  | @miljødirektoratet                 |
| 4   | 7TK                  | Tracks from large vehicles                       | Unitless, ordinal, non-linear scale from 1 to 4.                                        | Measures the frequency of imagined 100 m^2^ quadrats layed over the area that has some signs of vehicle tracks                                                    | @rune_halvorsen_dokumentasjon_2019 |
| 5   | PRTK                 | *as above*                                       | Unitless, ordinal, non-linear scale from 0 to 7.                                        | Same as 7TK, but recorded at a higher resolution                                                                                                                  | @miljødirektoratet                 |
| 6   | 7GR-GI               | Ditching intensity                               | Unitless, ordinal scale from 1 to 5                                                     | Describes the effect that drainage ditches is estimate to have on the species composition and environmental variables ones the system reached its new equilibrium | @miljødirektoratet                 |
| 7   | Infrastructure Index | Infrastructure Index                             | Unitelss linear scale from 0 to 13.2                                                    | Unitelss index ranging from from 0 to 13.2                                                                                                                        | @erikstad_index_2023               |
| 8   | HIA                  | Human Impact area                                | Ordinal, non-linear scale from 1 to 4                                                   | A categorical representation of the infrastructure index                                                                                                          | this paper                         |

@@

We chose three municipalities in Norway to test out the indicators (@fig-studyLocation).
These municipalities are spread over `r round(max(latlong$Y)-min(latlong$Y), 1)` degrees latitude, or `r km_distance` km, and also differ in the amount of mire area, the total area surveyed, and the prevalence of infrastructure (@tbl-variables).

@@

(temp <- readRDS("../figures/studyLocation.RDS"))
```

| Municipality | Total terrestrial area (km^2^)                                            | \% of terrestrial area surveyed                                            | \% open mires in relation to total terrestrial area                         | Total mire area (km^2^)                                                  | %of mire area inside survey area                                                      | Number of mire polygons in survey                                 | Mean Infrastructure Index value                                         |
|--------------|---------------------------------------------------------------------------|----------------------------------------------------------------------------|-----------------------------------------------------------------------------|--------------------------------------------------------------------------|---------------------------------------------------------------------------------------|-------------------------------------------------------------------|-------------------------------------------------------------------------|
| Nordre Follo | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(t_area_km)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(dk_percent)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(mirePercent)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(mire_km2)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(mireInSurvery_percent)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(n)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(meanHIA)` |
| Trondheim    | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(t_area_km)`    | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(dk_percent)`    |                                                                             |                                                                          |                                                                                       | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(n)`    | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(meanHIA)`    |
| Målselv      | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(t_area_km)`      | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(dk_percent)`      |                                                                             |                                                                          |                                                                                       | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(n)`      | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(meanHIA)`      |

@@

>>>>

```{r import}
#| eval: true
#| cache: true

@@

@@

```{r terraLoad}
#| eval: true
# Mire data
# Spat rasters cannot be cached
mire_terra <- terra::rast(path_mire)
```

@@

```{r mireTerra}
#| eval: false

# I first tried to import and crop the mire data using stars, but that failed (see pre 21 feb 2023)
# trying { terra } instead

@@

# Plot to check overlap
# ggplot()+
#  geom_spatraster(data = mire_nf_terra)+
#  geom_spatvector(data = nf_vect,
#                  fill = NA)
# The cropping and masking worked.
# 
# # I like the stars, sf and tmap combo better, so I return to stars
mire_stars_nf <- mire_terra_nf |>
  st_as_stars()
mire_stars_gr <- mire_terra_gr |>
  st_as_stars()
mire_stars_na <- mire_terra_na |>
  st_as_stars()

@@

saveRDS(mire_stars_nf, "manual_cache/mire_stars_nf.RDS")
saveRDS(mire_stars_gr, "manual_cache/mire_stars_gr.RDS")
saveRDS(mire_stars_na, "manual_cache/mire_stars_na.RDS")

@@

```{r terraToSTars}
#| eval: true
mire_stars_nf <- readRDS("manual_cache/mire_stars_nf.RDS")
mire_stars_gr <- readRDS("manual_cache/mire_stars_gr.RDS")
mire_stars_na <- readRDS("manual_cache/mire_stars_na.RDS")
```

```{r dk2-CoverageMaps}
#| eval: true
#| cache: true

@@

```{r mireArea}
#| eval: true
#| cache: true

@@

# Make a plot to check that it has worked
infraMuni3_tbl |>
  ggplot() +
  geom_bar(
    aes(
      x = infrastructureIndex,
      y = total_area_HIAs_km2,
      fill = factor(infrastructureIndex),
      colour = factor(infrastructureIndex)
    ),
    stat = "identity",
    lwd = 1.2
  ) +
  scale_fill_manual(values = RColorBrewer::brewer.pal(4, "YlOrBr")) +
  scale_color_manual(values = RColorBrewer::brewer.pal(5, "YlOrBr")[-1]) +
  theme_minimal_hgrid() +
  labs(
    x = "Human Impact Area (HIA) class",
    y = "Area (km<sup>2</sup>)"
  ) +
  theme(
    axis.title.x = element_textbox_simple(
      width = NULL,
      padding = margin(4, 4, 4, 4),
      margin = margin(4, 0, 0, 0),
      linetype = 1,
      r = grid::unit(8, "pt"),
      fill = "azure1"
    ),
    axis.title.y = element_textbox_simple(
      width = NULL,
      padding = margin(4, 4, 4, 4),
      margin = margin(4, 0, 0, 0),
      linetype = 1,
      orientation = "left-rotated",
      r = grid::unit(8, "pt"),
      fill = "azure1"
    ),
    strip.background = element_blank(),
    strip.text = element_textbox(
      size = 12,
      color = "white", fill = "#5D729D", box.color = "#4A618C",
      halign = 0.5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
      padding = margin(2, 0, 1, 0), margin = margin(3, 3, 3, 3)
    )
  ) +
  guides(fill = "none", colour = "none") +
  scale_y_log10() +
  facet_grid(cols = vars(Municipality))
```

```{r corrCheck}
#| eval: true
#| cache: true
# Now I want to see if the indicator values depend on the HIA is a predictable
# way to justify the stratification
corrCheck <- st_intersection(naturetypes, infra)

@@

```{r test 4}
#| eval: false
# The year effect is constant, so ignoring that
corrCheck |>
  mutate(
    i_ADSV_fct = floor(round(i_ADSV * 10, 2)) / 10,
    i_alien_fct = floor(round(i_alien * 10, 2)) / 10,
    i_ditch_fct = floor(round(i_ditch * 10, 2)) / 10
  ) |>
  pivot_longer(
    cols = c(i_ADSV_fct, i_alien_fct, i_ditch_fct),
    values_to = "indicatorValue",
    names_to = "indicator",
    values_drop_na = T
  ) |>
  ggplot(aes(
    x = factor(infrastructureIndex),
    fill = factor(indicatorValue)
  )) +
  geom_bar(
    position = "fill"
  ) +
  theme_bw(base_size = 12) +
  guides(fill = guide_legend("Scaled indicator values")) +
  ylab("Fraction of data points") +
  xlab("HIA") +
  scale_fill_brewer(
    palette = "RdYlGn") +
  facet_grid(~indicator)
```

```{r realValidationPlot}
#| eval: true
# Using a color gradient emphasizes the first color (dark green).
# Lets try discrete colors, and merge some classes to simplify
(validationPlot <- corrCheck |>
  pivot_longer(
    cols = c(i_ADSV, i_alien, i_ditch),
    values_to = "indicatorValue",
    names_to = "indicator",
    values_drop_na = T
  ) |>
  mutate(
    condition = case_when(
      indicatorValue < 0.6 ~ "<0.6",
      indicatorValue < 0.8 ~ "0.6 to 0.8",
      indicatorValue < 0.91 ~ "0.8 to 0.9",
      .default = "0.9 to 1"
    ),
    condition = fct_reorder(condition, indicatorValue),
    indicator = case_when(
      indicator == "i_ADSV" ~ "ADSV",
      indicator == "i_alien" ~ "Alien species",
      indicator == "i_ditch" ~ "Trenching"
    )
  ) |>
  as_tibble() |>
  group_by(indicator, infrastructureIndex, condition) |>
  summarise(n = n()) |>
  ungroup() |>
  group_by(indicator, infrastructureIndex) |>
  mutate(lab = round(n/sum(n)*100),
         lab = case_when(
           lab < 5 ~ NA,
           .default = paste0(lab, "%")
         )) |>
  ggplot(aes(
    x = infrastructureIndex,
    y = n,
    fill = condition
  )) +
  geom_bar(
    position = "fill",
    stat = "identity"
  ) +
  geom_text(aes(label = lab),
    position = position_fill(vjust = 0.5),
    color= "black", vjust = 0.5, size = 4) +
  theme_minimal(base_size = 15) +
  theme(
    panel.grid = element_blank(), 
    axis.text.x = element_text(margin = margin(t = -10)),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    strip.text = element_textbox(
      size = 12,
      halign = 0.5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
      padding = margin(2, 0, 1, 0), margin = margin(3, 3, 3, 3))) +
  guides(fill = guide_legend("Indicator values")) +
  xlab("Human Impact Areas") +
  scale_fill_manual(values = c("#E85437","#FBAF00", "#B5DF73", "#009000")) +
  facet_grid(~indicator)
)
```

```{r test3}
#| eval: false
# The figure changes a lot depending on which value gets the darker colour
corrCheck |>
  pivot_longer(
    cols = c(i_ADSV, i_alien, i_ditch),
    values_to = "indicatorValue",
    names_to = "indicator",
    values_drop_na = T
  ) |>
  mutate(
    condition = case_when(
      indicatorValue < 0.6 ~ "Poor",
      indicatorValue < 0.8 ~ "Intermediate",
      indicatorValue < 0.91 ~ "Good",
      .default = "Perfect"
    ),
    condition = fct_reorder(condition, -indicatorValue)
  ) |>
  ggplot(aes(
    x = factor(infrastructureIndex),
    fill = condition
  )) +
  geom_bar(
    position = "fill"
  ) +
  theme_bw(base_size = 12) +
  guides(fill = guide_legend("Scaled indicator values")) +
  ylab("Fraction of data points") +
  xlab("HIA") +
  scale_fill_viridis_d(alpha = .8) +
  facet_grid(~indicator)
```

```{r test2}
#| eval: false
# If I look at this on a log scale, it also changes and becomes less convincing for ADSV and alien
corrCheck |>
  pivot_longer(
    cols = c(i_ADSV, i_alien, i_ditch),
    values_to = "indicatorValue",
    names_to = "indicator",
    values_drop_na = T
  ) |>
  mutate(
    condition = case_when(
      indicatorValue < 0.6 ~ "Poor",
      indicatorValue < 0.8 ~ "Intermediate",
      indicatorValue < 0.91 ~ "Good",
      .default = "Perfect"
    ),
    condition = fct_reorder(condition, -indicatorValue)
  ) |>
  ggplot(aes(
    x = factor(infrastructureIndex),
    fill = condition
  )) +
  geom_bar(
    position = "fill"
  ) +
  theme_bw(base_size = 12) +
  guides(fill = guide_legend("Scaled indicator values")) +
  ylab("Fraction of data points") +
  xlab("HIA") +
  scale_y_log10() +
  scale_fill_viridis_d(alpha = .8) +
  facet_grid(~indicator)

@@

```{r test}
#| eval: false

@@

```{r infraMuniMaps}
#| eval: true
#| cache: true

# Infratructure in each municipality
(infraMuniMap <- tm_shape(muni3) +
  tm_borders() +
  tm_shape(infraMuni3) +
  tm_polygons(
    col = "infrastructureIndex",
    style = "cat",
    title = "Human Impact Areas"
  ) +
  tm_layout(
    legend.show = F,
    panel.label.height = 0) +
  tm_shape(muni3) +
  tm_borders(lwd = 3, col = "black") +
  tm_facets(by = "Municipality"))

# A figure with just the legend
infraMuniMap_l <- tm_shape(muni3) +
  tm_borders() +
  tm_shape(infraMuni3) +
  tm_polygons(
    col = "infrastructureIndex",
    style = "cat",
    title = "Human\nImpact\nArea"
  ) +
  tm_layout(legend.only = TRUE,
            legend.position = c("left", "bottom"),
            legend.outside = F)

empty <- tm_shape(muni3) +
  tm_borders(col="white") +
  tm_layout(frame = F)

@@

(methodsMap <- tmap_arrange(
  muniPlot,
  empty,
  infraMuniMap,
  infraMuniMap_l,
  ncol = 2,
  widths = c(.8, .2),
  heights = c(.6, .4),
  outer.margins = NULL
))

@@

# Calculate some more stats for the table with municipality stats

@@

# Take muni3 and add all sorts of other data to it
# using left_join.
# Save local cached file
muni_tbl <- muni3 |>
  # calculate total area
  mutate(
    area_km =
      round(
        units::drop_units(
          geom |> st_area() * 1e-6
        )
      )
  ) |>
  # make tibble for the coming join
  as_tibble() |>
  # paste inn terrestrial area
  left_join(
    terrestrial |>
      as_tibble() |>
      select(kommunenummer, t_area_km),
    keep = F
  ) |>
  # area of survey
  left_join(dk2 |> select(Municipality, dk_area_km)) |>
  mutate(dk_percent = round((dk_area_km / t_area_km) * 100)) |>
  # number of polygons
  left_join(nature3_tbl |> select(Municipality, n)) |>
  # total mire area and %
  left_join(mireArea |> select(Municipality, mirePercent, mire_km2)) |>
  # % mire inside survey coverage map
  left_join(mire_in_dk |> select(Municipality, mireInSurvey_km2)) |>
  mutate(mireInSurvery_percent = round(mireInSurvey_km2 / mire_km2 * 100, 2)) |>
  left_join(infraMuni3_summary)

@@

| id  | Variable code        | Variable name                                    | Measurement unit                                                                        | Description                                                                                                                                                       | Reference                          |
|------------|------------|------------|------------|----------------|------------|
| 1   | 7FK                  | Prevalence of alien species                      | Unitless, ordinal, non-linear scale from 1 (no alien species) to 7 (only alien species) | The fraction of the species composition made up from alien species                                                                                                | @runehalvorsen2019                 |
| 2   | 7SE                  | Human caused abration or abration-caused erosion | Unitless, ordinal, non-linear scale from 1 to 4.                                        | Measures the frequency of imagined 4 m^2^ quadrats layed over the area that has some sign of abration                                                             | @runehalvorsen2019                 |
| 3   | PRSL                 | *as above*                                       | Unitless, ordinal, non-linear scale from 0 to 7.                                        | Same as 7SE, but recorded at a higher resolution                                                                                                                  | @miljødirektoratet                 |
| 4   | 7TK                  | Tracks from large vehicles                       | Unitless, ordinal, non-linear scale from 1 to 4.                                        | Measures the frequency of imagined 100 m^2^ quadrats layed over the area that has some signs of vehicle tracks                                                    | @rune_halvorsen_dokumentasjon_2019 |
| 5   | PRTK                 | *as above*                                       | Unitless, ordinal, non-linear scale from 0 to 7.                                        | Same as 7TK, but recorded at a higher resolution                                                                                                                  | @miljødirektoratet                 |
| 6   | 7GR-GI               | Ditching intensity                               | Unitless, ordinal scale from 1 to 5                                                     | Describes the effect that drainage ditches is estimate to have on the species composition and environmental variables ones the system reached its new equilibrium | @miljødirektoratet                 |
| 7   | Infrastructure Index | Infrastructure Index                             | Unitelss linear scale from 0 to 13.2                                                    | Unitelss index ranging from from 0 to 13.2                                                                                                                        | @erikstad_index_2023               |
| 8   | HIA                  | Human Impact area                                | Ordinal, non-linear scale from 1 to 4                                                   | A categorical representation of the infrastructure index                                                                                                          | this paper                         |

@@

We chose three municipalities in Norway to test out the indicators (@fig-studyLocation).
The differ in several aspect, such as the amount of mire area, the total area surveyed, and the prevalence of infrastructure (@tbl-variables).

@@

#(temp <- readRDS("../figures/studyLocation.RDS"))
positionMap
```

```{r fig-studyLocation2}
#| eval: true
#| include: true
#| out.width: '100%'
#| fig.cap:
#| - "Map of the three focal municiaplities. For each municipality the map shows 
#| ocean in blue and non-ocean
#| in green. The survey coverage maps are in grey, and the mapped mires are
#| in red, with polygon borderes made extra thich to make them visible,
#| but then also exagerating their size."

#(temp <- readRDS("../figures/studyLocation.RDS"))
methodsMap
```

| Municipality  | Total terrestrial area (km^2^)                                            | \% of terrestrial area surveyed                                            | \% open mires in relation to total terrestrial area                         | Total mire area (km^2^)                                                  | %of mire area inside survey area                                                      | Number of mire polygons in survey                                 | Mean Infrastructure Index value                                         |
|---------|---------|---------|---------|---------|---------|---------|---------|
| Nordre Follo  | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(t_area_km)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(dk_percent)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(mirePercent)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(mire_km2)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(mireInSurvery_percent)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(n)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(meanHIA)` |
| `Gran`        | `r muni_tbl |> filter(Municipality == "Gran") |> pull(t_area_km)`         | `r muni_tbl |> filter(Municipality == "Gran") |> pull(dk_percent)`         | `r muni_tbl |> filter(Municipality == "Gran") |> pull(mirePercent)`         | `r muni_tbl |> filter(Municipality == "Gran") |> pull(mire_km2)`         | `r muni_tbl |> filter(Municipality == "Gran") |> pull(mireInSurvery_percent)`         | `r muni_tbl |> filter(Municipality == "Gran") |> pull(n)`         | `r muni_tbl |> filter(Municipality == "Gran") |> pull(meanHIA)`         |
| `Nord-Aurdal` | `r muni_tbl |> filter(Municipality == "Nord-Aurdal") |> pull(t_area_km)`  | `r muni_tbl |> filter(Municipality == "Nord-Aurdal") |> pull(dk_percent)`  | `r muni_tbl |> filter(Municipality == "Nord-Aurdal") |> pull(mirePercent)`  | `r muni_tbl |> filter(Municipality == "Nord-Aurdal") |> pull(mire_km2)`  | `r muni_tbl |> filter(Municipality == "Nord-Aurdal") |> pull(mireInSurvery_percent)`  | `r muni_tbl |> filter(Municipality == "Nord-Aurdal") |> pull(n)`  | `r muni_tbl |> filter(Municipality == "Nord-Aurdal") |> pull(meanHIA)`  |

@@

```{r fig-validation}
#| eval: true
#| include: true
#| out.width: '100%'
#| fig.cap:
#| - "Proportion of localities with different scaled indicator values for three 
#| ecosystem condition indicators along a Human Impact Gradient"

validationPlot
```
